ParaChiCSVO2

### 2024-05-24 index.tex
rendered

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3014}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2055}}@{}}
\caption{Technical parameters for MR imaging
protocol.}\label{tbl-mri}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T1w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T2w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
pcASL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
SWI
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T1w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T2w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
pcASL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
SWI
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Sequence & 3D FSPGR & 3D CUBE & Multi-shot 3D
\textbackslash\textbackslash{} fast spin-echo & 3D spoiled GRE
flow-compensated \\
Phase-encoding direction & Coronal & Sagittal & Axial & Axial \\
TR (ms) & 7.74 & 2,300 & 4,680 & 30.9 \\
TE (ms) & 2.97 & 66.29 & 10.55 & 5.24 \\
Flip angle & 12\(^{\circ}\) & 90\(^{\circ}\) & 111\(^{\circ}\) &
20\(^{\circ}\) \\
FOV (cm) & 20 & 20 & 24 & 25 \\
Acquisition Matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256 \\
In-plane resolution (mm) & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 &
0.977 x 0.977 \\
Slice thickness (mm) & 1 & 1 & 4 & 2, reconstructed to 1 mm with zero
filling (ZIP2) \\
Number of slices & 126 & 106 & 50 & 92 \\
Additional parameters & n/a & n/a & 1,450 ms label period; 2,025 ms
pulse lable; 24 control-label pairs & n/a \\
Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s \\
\end{longtable}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1644}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.3014}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2055}}@{}}
\caption{Technical parameters for MR imaging
protocol.}\label{tbl-mri}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T1w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T2w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
pcASL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
SWI
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T1w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
T2w
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
pcASL
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
SWI
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Sequence & 3D FSPGR & 3D CUBE & Multi-shot 3D fast spin-echo & 3D
spoiled GRE flow-compensated \\
Phase-encoding direction & Coronal & Sagittal & Axial & Axial \\
TR (ms) & 7.74 & 2,300 & 4,680 & 30.9 \\
TE (ms) & 2.97 & 66.29 & 10.55 & 5.24 \\
Flip angle & 12\(^{\circ}\) & 90\(^{\circ}\) & 111\(^{\circ}\) &
20\(^{\circ}\) \\
FOV (cm) & 20 & 20 & 24 & 25 \\
Acquisition Matrix & 512 x 512 & 256 x 256 & 128 x 128 & 256 x 256 \\
In-plane resolution (mm) & 0.39 x 0.39 & 0.78 x 0.78 & 1.875 x 1.875 &
0.977 x 0.977 \\
Slice thickness (mm) & 1 & 1 & 4 & 2, reconstructed to 1 mm with zero
filling (ZIP2) \\
Number of slices & 126 & 106 & 50 & 92 \\
Additional parameters & n/a & n/a & 1,450 ms label period; 2,025 ms
pulse lable; 24 control-label pairs & n/a \\
Scan duration & 4 min 39 s & 5 min 1 s & 5 min 26 s & 5 min 29 s \\
\end{longtable}
